Parenting Observational Study E2

### 2019-02-27 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
add JA data and info data

---
title: "Parenting Observational Study"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

@@

  id <- data.frame(SID = SID,
                   line = line,
                   phase_onset = phase_onset,
                   phase_offset = phase_offset, 
                   pja = pja,
                   cja = cja,
                   bid = bid)

  l_pja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(pja == 1)%>%
    group_by(SID, pja)%>%
    summarise(pja_length = sum(phase_length))%>%
    select(-pja)

  l_cja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(cja == 1)%>%
    group_by(SID, cja)%>%
    summarise(cja_length = sum(phase_length))%>%
    select(-cja)

  c_pja <- id%>%
    group_by(SID)%>%
    summarise(pja = sum(pja))

  c_cja <- id%>%
    group_by(SID)%>%
    summarise(cja = sum(cja))

  c_bids <- id%>%
    group_by(SID)%>%
    summarise(bids = sum(bid))

@@

Read in trial info and demographics.

```{r}
conditions <- read.csv("conditions.csv")

load("../paq/paq_demo.RData")
load("../paq/obs_demo.RData")

ids <- ids%>%
  mutate(SID = sid)%>%
  select(-sid)

demo <- demo%>%
  mutate(SID = sid)%>%
  select(-sid)%>%
  mutate(age_months = age * 12)

demo$age_group[demo$age_months < 12] <- "6"
demo$age_group[demo$age_months >= 12 & demo$age_months < 18 ] <- "12"
demo$age_group[demo$age_months >= 18] <- "18"

#note from Emily- I calculated total bids by adding unsuccessful bids + episodes of joint attention that were acheived. In retrospect, this assumes that all episodes of JA were initiated by parent, which is probably false. Next time, code all parent bids rather than only unsuccessful ones.
d <- d.raw %>%
  left_join(conditions)%>%
  mutate(bids_tot = bids + cja + pja)%>%
  left_join(demo)%>%
  left_join(ids)%>%
  select(-sid)
```

#Demographics

```{r}
demos <- conditions%>%
  left_join(demo)

demos$parent_ed[demos$parent_ed == 1] <- 8
demos$parent_ed[demos$parent_ed == 2] <- 12
demos$parent_ed[demos$parent_ed == 3] <- 14
demos$parent_ed[demos$parent_ed == 4] <- 18
demos$parent_ed[demos$parent_ed == 5] <- 20
demos$parent_ed[demos$parent_ed == 6] <- 22

#child gender
table(demos$Condition, demos$gender)
#ethnicity
table(demos$Condition, demos$ethnicity)
#years of education
table(demos$Condition, demos$parent_ed)
```

@@

  id <- data.frame(SID = SID,
                   line = line,
                   phase_onset = phase_onset,
                   phase_offset = phase_offset, 
                   pja = pja,
                   cja = cja,
                   bid = bid)

  l_pja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(pja == 1)%>%
    group_by(SID, pja)%>%
    summarise(pja_length = sum(phase_length))%>%
    select(-pja)

  l_cja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(cja == 1)%>%
    group_by(SID, cja)%>%
    summarise(cja_length = sum(phase_length))%>%
    select(-cja)

  c_pja <- id%>%
    group_by(SID)%>%
    summarise(pja = sum(pja))

  c_cja <- id%>%
    group_by(SID)%>%
    summarise(cja = sum(cja))

  c_bids <- id%>%
    group_by(SID)%>%
    summarise(bids = sum(bid))

@@

Reliability.
```{r}
d.raw_rel <- d.raw_rel%>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length)%>%
  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

@@

Total number of bids (successful and unsuccessful)
```{r, width=4, height=4}
save(d, file="Exp1_joint_attention_data.RData")
ms_bids <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "bids_tot")

ms_bids$Condition <- factor(ms_bids$Condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.position="none") 
```

@@

```{r}
ms_tja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "total_ja")

ms_tja$Condition <- factor(ms_tja$Condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total episodes of Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Episodes of passive joint attention.
```{r}
ms_pja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Episodes of coordinated joint attention
```{r}
ms_cja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Total duration of passive joint attention.
```{r}
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Total duration of coordinated joint attention.
```{r}
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

>>>>

---
title: "Parenting Observational Study E2"
author: "Emily, Vivian"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

@@

  id <- data.frame(sid = SID,
                   line = line,
                   phase_onset = phase_onset,
                   phase_offset = phase_offset, 
                   pja = pja,
                   cja = cja,
                   bid = bid)

  # Only count the JA more than 3 seconds
  l_pja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter((phase_length >3000)&(pja == 1))%>%
    group_by(sid, pja)%>%
    summarise(pja_length = sum(as.numeric(phase_length)))%>%
    select(-pja)

  l_cja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter((phase_length >3000)&(cja == 1))%>%
    group_by(sid, cja)%>%
    summarise(cja_length = sum(as.numeric(phase_length)))%>%
    select(-cja)

  c_pja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(phase_length >3000)%>%
    group_by(sid)%>%
    summarise(pja = sum(as.numeric(pja)))

  c_cja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(phase_length >3000)%>%
    group_by(sid)%>%
    summarise(cja = sum(as.numeric(cja)))

  c_bids <- id%>%
    group_by(sid)%>%
    summarise(bids = sum(as.numeric(bid)))

@@

Read in trial info 
```{r}
conditions <- read.csv("conditions.csv")

#note from Emily- I calculated total bids by adding unsuccessful bids + episodes of joint attention that were acheived. In retrospect, this assumes that all episodes of JA were initiated by parent, which is probably false. Next time, code all parent bids rather than only unsuccessful ones.

d <- left_join(d.raw, conditions, by = "sid")
d$condition [d$sid=="111517_3"] = "exp"
d$video [d$sid=="111517_3"] = "big_small"
d$age [d$sid=="111517_3"] = "2"
```

@@

  id <- data.frame(sid = SID,
                   line = line,
                   phase_onset = phase_onset,
                   phase_offset = phase_offset, 
                   pja = pja,
                   cja = cja,
                   bid = bid)

  l_pja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter((phase_length >3000)&(pja == 1))%>%
    group_by(sid, pja)%>%
    summarise(pja_length = sum(as.numeric(phase_length)))%>%
    select(-pja)

  l_cja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter((phase_length >3000)&(cja == 1))%>%
    group_by(sid, cja)%>%
    summarise(cja_length = sum(as.numeric(phase_length)))%>%
    select(-cja)

  c_pja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(phase_length >3000)%>%
    group_by(sid)%>%
    summarise(pja = sum(as.numeric(pja)))

  c_cja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(phase_length >3000)%>%
    group_by(sid)%>%
    summarise(cja = sum(as.numeric(cja)))

  c_bids <- id%>%
    group_by(sid)%>%
    summarise(bids = sum(bid))

@@

Reliability.
```{r}
d.raw_rel <- d.raw_rel%>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length)%>%
  select(sid, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

@@

Total number of bids (successful and unsuccessful)
```{r, width=4, height=4}
save(d, file="Exp2_joint_attention_data.RData")
ms_bids <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "bids")

ms_bids$condition <- factor(ms_bids$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_bids, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.position="none") 
```

@@

```{r}
ms_tja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "total_ja")

ms_tja$Condition <- factor(ms_tja$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_tja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total episodes of Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Episodes of passive joint attention.
```{r}
ms_pja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Episodes of coordinated joint attention
```{r}
ms_cja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Total duration of passive joint attention.
```{r}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Total duration of coordinated joint attention.
```{r}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```
